Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-03-08 paper.tex
First outline
More notes
test

@@

@@

@@

% Summarize Koren, Bell and Volinsky: https://dl.acm.org/citation.cfm?id=1608614
% Explain that you have binary classes (rounding)
% Biases

@@

% Present your results: accuracy, ROC curves, transparency matrix.

@@

@@

>>>>

Computational reproducibility, the property through which
computational results can be recomputed over time and
space~\cite{stodden}, has become a critical component of scientific
methodology with the rise of the reproducibility crisis in several
domains~\cite{xxx}. Among the factors hampering computational
reproducibility, infrastructural characteristics such as the operating
system play an important role. In neurosciences, our primary field of
interest, several studies have shown the effect of the operating
system on computational results. However, conducting such
reproducibility studies at scale is cumbersome due to the execution
time of data analysis pipelines, which easily exceeds a few hours.

In this paper we investigate approximate methods to predict the
reproducibility of a computational analysis from the first files that
it produces. Our main intuition is that reproducibility errors are
caused by a reduced number of factors that originate in the analysis
pipeline and input data.

@@

% Refer to Germain et al 2008.

@@

what is specific to our problem compared to regular collaborative filtering:
%+ subjects are equivalent to users. Not all subjects have the same input data. Anatomical variability, acquisition variability (e.g., 1 subject may have multiple T1s).
%+ files are produced in a specific order (movies aren't),
% which add constraints on the training set (cannot sample late files and not early ones).
%+ utility matrix is not sparse: we can potentially populate it completely. Which means that we can decide precisely which samples we need (active sampling). Therefore we can take the first row and first column to avoid cold start issues.

@@

% Summarize Koren, Bell and Volinsky: https://dl.acm.org/citation.cfm?id=1608614

% Explain that you have binary classes (rounding)

% Biases

@@

% Present your results: accuracy, ROC curves, transparency matrix, factors.

% Try with different numbers of factors.

@@

% Not all subjects behave the same, which motivates the Big Data approach.

@@

% Interpreting the factors? Factors reflect the pipeline definition.
